Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2025-01-06 paper/tex/paper.tex
Update paper

Litrepl is a lightweight text processing tool designed to recognize and evaluate
code sections within Markdown or \Latex documents. This functionality is useful
for both batch document section evaluation and interactive coding within a text
editor, provided a straightforward integration is established.

>>>>

Litrepl is a lightweight text processing tool designed to recognize and evaluate
code sections within Markdown or \Latex documents. This functionality is useful
for both batch document section evaluation and interactive coding within a text
editor, provided a straightforward integration is established. Inspired by
Project Jupyter, it aims to facilitate the creation of research documents. In
the light of recent developments in software deployment, however, we have
shifted our focus from ad-hoc reproducibility to enhancing transparency in
communication with programming language interpreters, by either eliminating or
clearly exposing mutable states within the communication process.
